\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-26 paper.tex
all updated

(2) $\mathsf{BATE}$ achieves a good tradeoff between efficiency and optimality. 
Compared with the optimal solutions, (i) our admission control algorithm can speed up the admission procedure by 30$\times$ at the expense of less than 4\% false rejections, 
(ii) our pruning-augmented scheduling algorithm runs $10^2 \sim 10^4 \times$ faster while wasting only 6\% total bandwidth, 
and (iii) our greedy failure recovery algorithm can reduce the reaction time by xx$\times$, 
where profit loss is only around 10\%.

@@

\subsection{Simulations}
\textbf{Simulation setup.} 
We also conduct simulations on four real network topologies, including B4 \cite{B4}, ATT \cite{Teavar}, IBM\cite{SMORE} and a national-level backbone. 
Table \ref{evaluation-topologies} shows the topology details
\footnote{For B4, ATT and IBM, we get their topologies, link capacities and traffic matrices from the authors of TEAVAR\cite{Teavar}, and for the national backbone, we conduct a direct measurement on it but hide its name due to anonymity requirement.}. 
Following the conclusion on WAN failures in literature studies\cite{Characterization, Teavar}, 
we simulate link failures according to a Weibull distribution with its shape $\lambda=0.8$ and scale $k=0.00001$. 
We generate the demand workload in a similar way to that in the testbed. 
The arrivals of BA demands follow a Poisson process, where the mean arrival rate varies from 1 to 5 in each time slot. 
The duration of each demand follows an exponential distribution, and the mean duration corresponds to 1000 time slots.
The required bandwidth in each user demand is randomly drawn from the traffic metrices (we have collected 200 matrices for each topology) with a proper scale down factor\footnote{We use a factor of 5, and a mean arrival rate of 5 in our simulation corresponds to the normal network load.}, so that between each source-destination pair, multiple users can be served simultaneously. 
The required availability in each user demand is drawn from 10 different SLAs of Azure\cite{azure}.
In our simulations, besides FFC and TEAVAR, we also compare against several other TE algorithms,  
including SWAN \cite{swan}, SMORE \cite{SMORE} and B4 \cite{B4}. 
They have not explicitly considered availability, but pay attention to 
total throughput, link utilization or user fairness. 
These TE algorithms will be activated every 10 time slots.
We assume at most one link failure (i.e., no concurrent failures) in FFC,  
use 99.9\% (which is the maximum value in the user demands) as the default availability target in TEAVAR,
and let SWAN maximize the total throughput of all users. 
With the above settings, each simulation lasts 150,000 slots (corresponding to 100 days if each slot represents 1 minute), and the results achieved by each algorithm on each topology are calculated on 5 independent simulations with different workload traces. 
All the simulations are conducted on a Linux server with a quad-core 2.60GHz processor and 32GB memory.

@@

We then compare the traffic scheduling capability of $\mathsf{BATE}$ against FFC, TEAVAR, SWAN, SMORE and B4.
The methodology is similar to the post-processing simulation in TEAVAR \cite{Teavar}, 
where we simulate different failure scenarios according to their probabilities, 
and in each scenario we record the demands that can be satisfied. 
If the \textit{achieved availibility}, i.e., the total posterior probabilities of \textit{qualified} scenarios where a user's bandwidth target is met, is larger than the user's availability target, 
then the BA demand is \textit{satisfied}. 
We plot the overall percentage of satisfied BA demands under each arrival rate (averaged across all simulations) in Figure \ref{scheduling-benefit}(a). $\mathsf{BATE}$ nearly always achieves a satisfaction ratio around 100\%, with a leading margin of at least 23\% (with respect to TEAVAR) under a high arrival rate (rate=6 in the figure)\footnote{$\mathsf{BATE}$ leads FFC by around 60\%, which is not shown in the figure.}. 
To further demonstrates $\mathsf{BATE}$'s advantage in matching stringent availability requirements  
with reliable links, we further augment each TE algorithm with the \textit{fixed} admission control 
scheme. The satisfaction ratios are plotted in Figure \ref{scheduling-benefit}(b), where $\mathsf{BATE}$
still performs at least 10\% better than the others.

\iffalse
%We write down the bandwidth loss of each scenario for each demand and each scenario's corresponding probability.
The sum of scenario probability where demand is fully satisfied reflects the \textit{achieved availability}.
%If a demand's , then the availability defined in SLA is \textit{satisfaction}.
The term \textit{satisfaction percentage} refers to the fraction of total arrival demands whose achieved availability are higher than their availability targets throughout duration.
Figure \ref{scheduling-benefit}(a) demonstrates that $\mathsf{BATE}$ can even make up to 40\% more demands satisfy SLA availability.
%Demands SLA violation of  $\mathsf{BATE}$ mainly comes from admission control rejection.
%The reason for this is that $\mathsf{BATE}$ adopts admission control and it considers the diverse availability targets of different bandwidth demands.
$\mathsf{BATE}$ can make demands with stringent availability requirements pass links with high reliability, therefore, their availability targets can be guaranteed, but other schemes are unable differentiate demands.
To show this benefit, we adopt \textit{Fixed} admission control for each traffic scheduling algorithm, then Figure \ref{scheduling-benefit}(b) shows $\mathsf{BATE}$ performs at least 10\% better than other algorithms under the \textit{Fixed} admission control method.
\fi
\begin{figure}[t]
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/evaluation/sim-monney.pdf}
\caption{Profit gain after failures}
\label{sim-profit}
\end{center}
\end{figure}
Figure \ref{sim-profit} shows the average profit after failures occur in the network.
Due to its considration of pricing and refunding,  
$\mathsf{BATE}$ is able to retain 10\%$\sim$20\% more profit than the other algorithms.
\footnote{Our preliminary results show $\mathsf{BATE}$ will perform even better than the others under more complicated multi-stage SLAs, especially when the refunding ratio $\mu=1$ under low satisfaction.}

Remeber that our scaling down factor is 5, so these summarized results are all collected under normal network load, where the mean arrival rate in each slot is between 1 and 6. 
We note that, under heavier loads, $\mathsf{BATE}$ performs even better than its competitors, 
but we regard that as less possible in reality.

@@

Finally, we compute the approximation ratio of our greedy failure recovery algorithm, 
which is defined as dividing the optimal profit by the profit achieved. 
Figure \ref{approximation} shows that, 
our 2-approximation algorithm achieves a ratio between 1 and 1.25 in real scenarios, 
and the average profit loss is around 10\% and it can save at least 90\% time (more details can be seen in Appendix \ref{testbed-appendix}).
%Satisfaction percentage. It denotes the percentages of applications whose achieved availability is larger than the corresponding target.
%Figure \ref{availability_fig1}(b) shows 
%$\mathsf{BATE}$ performs about 20\%, 25\%, 30\%,  40\% better than TEAVAR, SMORE, SWAN, FFC, respectively.
%%Specially, when traffic scale is 3, more than 70\% applications can satisfy their availability demands, which is at least 30\% better than TEAVAR.
%Specially, the advantage of $\mathsf{BATE}$  is more obvious when there are resource competition (e.g., $s=3$).
%%The reason for this is that $\mathsf{BATE}$ considers the bandwidth-based availability demand differentiation of applications.
%This picture also demonstrates that the performance of $\mathsf{BATE}$ doesn't depend on particular network topology and traffic.
%Next, we take IBM trace as the example and perform the experiments.

@@

We compute the time ratio of the optimal solution and our greedy failure recovery algorithm for each scenario.
Figure \ref{sim-time}  shows that the optimal solution which is derived by bruce force algorithm is at least 9 $\times$ larger than our greedy failure recovery algorithm.
\end{appendices}

>>>>

(2) $\mathsf{BATE}$ achieves a good tradeoff between efficiency and optimality. 
Compared with the optimal solutions, (i) our admission control algorithm can speed up the admission procedure by 30$\times$ at the expense of less than 4\% false rejections, 
(ii) our pruning-augmented scheduling algorithm runs $10^2 \sim 10^4 \times$ faster while wasting only 6\% total bandwidth, 
and (iii) our greedy failure recovery algorithm can reduce the reaction time by 100$\times$, 
where profit loss is only around 10\%.

@@

\subsection{Simulations}
\textbf{Simulation setup.} 
We also conduct simulations on four real network topologies, including B4 \cite{B4}, ATT \cite{Teavar}, IBM\cite{SMORE} and a national-level backbone. 
Table \ref{evaluation-topologies} shows the topology details
\footnote{For B4, ATT and IBM, we get their topologies, link capacities and traffic matrices from the authors of TEAVAR\cite{Teavar}, and for the national backbone, we conduct a direct measurement on it but hide its name due to anonymity requirement.}. 
Following the conclusion on WAN failures in literature studies\cite{Characterization, Teavar}, 
we simulate link failures according to a Weibull distribution with its shape $\lambda=0.8$ and scale $k=0.00001$. 
We generate the demand workload in a similar way to that in the testbed. 
The arrivals of BA demands follow a Poisson process, where the mean arrival rate varies from 1 to 5 in each time slot. 
The duration of each demand follows an exponential distribution, and the mean duration corresponds to 1000 time slots.
The required bandwidth in each user demand is randomly drawn from the traffic metrices (we have collected 200 matrices for each topology) with a proper scale down factor\footnote{We use a factor of 5, and a mean arrival rate around 5 in our simulation corresponds to the normal network load.}, so that between each source-destination pair, multiple users can be served simultaneously. 
The required availability in each user demand is drawn from 10 different SLAs of Azure\cite{azure}.
In our simulations, besides FFC and TEAVAR, we also compare against several other TE algorithms,  
including SWAN \cite{swan}, SMORE \cite{SMORE} and B4 \cite{B4}. 
They have not explicitly considered availability, but pay attention to 
total throughput, link utilization or user fairness. 
These TE algorithms will be activated every 10 time slots.
We assume at most one link failure (i.e., no concurrent failures) in FFC,  
use 99.9\% (which is the maximum value in the user demands) as the default availability target in TEAVAR,
and let SWAN maximize the total throughput of all users. 
With the above settings, each simulation lasts 150,000 slots (corresponding to 100 days if each slot represents 1 minute), and the results achieved by each algorithm on each topology are calculated on 5 independent simulations with different workload traces. 
All the simulations are conducted on a Linux server with a quad-core 2.60GHz processor and 32GB memory.

@@

We then compare the traffic scheduling capability of $\mathsf{BATE}$ against FFC, TEAVAR, SWAN, SMORE and B4.
The methodology is similar to the post-processing simulation in TEAVAR \cite{Teavar}, 
where we simulate different failure scenarios according to their probabilities, 
and in each scenario we record the demands that can be satisfied. 
If the \textit{achieved availibility}, i.e., the total posterior probabilities of \textit{qualified} scenarios where a user's bandwidth target is met, is larger than the user's availability target, 
then the BA demand is \textit{satisfied}. 
We plot the overall percentage of satisfied BA demands under each arrival rate (averaged across all simulations) in Figure \ref{scheduling-benefit}(a). $\mathsf{BATE}$ nearly always achieves a satisfaction ratio around 100\%, with a leading margin of at least 23\% (with respect to TEAVAR) under a normal arrival rate (rate=6 in the figure)\footnote{$\mathsf{BATE}$ leads FFC by around 60\%, which is not shown in the figure.}. 
To further demonstrates $\mathsf{BATE}$'s advantage in matching stringent availability requirements  
with reliable links, we further augment each TE algorithm with the \textit{fixed} admission control 
scheme. The satisfaction ratios are plotted in Figure \ref{scheduling-benefit}(b), where $\mathsf{BATE}$
still performs at least 10\% better than the others (rate=6).

\iffalse
%We write down the bandwidth loss of each scenario for each demand and each scenario's corresponding probability.
The sum of scenario probability where demand is fully satisfied reflects the \textit{achieved availability}.
%If a demand's , then the availability defined in SLA is \textit{satisfaction}.
The term \textit{satisfaction percentage} refers to the fraction of total arrival demands whose achieved availability are higher than their availability targets throughout duration.
Figure \ref{scheduling-benefit}(a) demonstrates that $\mathsf{BATE}$ can even make up to 40\% more demands satisfy SLA availability.
%Demands SLA violation of  $\mathsf{BATE}$ mainly comes from admission control rejection.
%The reason for this is that $\mathsf{BATE}$ adopts admission control and it considers the diverse availability targets of different bandwidth demands.
$\mathsf{BATE}$ can make demands with stringent availability requirements pass links with high reliability, therefore, their availability targets can be guaranteed, but other schemes are unable differentiate demands.
To show this benefit, we adopt \textit{Fixed} admission control for each traffic scheduling algorithm, then Figure \ref{scheduling-benefit}(b) shows $\mathsf{BATE}$ performs at least 10\% better than other algorithms under the \textit{Fixed} admission control method.
\fi
\begin{figure}[t]
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/evaluation/sim-monney.pdf}
\caption{Profit gain after failures}
\label{sim-profit}
\end{center}
\end{figure}
Figure \ref{sim-profit} shows the average profit after failures occur in the network.
Due to its considration of pricing and refunding,  
$\mathsf{BATE}$ is able to retain 10\%$\sim$20\% more profit than the other algorithms
\footnote{Our preliminary results show $\mathsf{BATE}$ will perform even better than the others under more complicated multi-stage SLAs, especially when the refunding ratio $\mu=1$ under low satisfaction.}.

Remeber that our scaling down factor is 5, so our summarized key results are for a normal network load, where the mean arrival rate in each slot is 5$\sim$6. 
We note that, under heavier loads, $\mathsf{BATE}$ performs even better than its competitors, 
but we regard that as less possible in reality.

@@

Finally, we compute the approximation ratio of our greedy failure recovery algorithm, 
which is defined as dividing the optimal profit by the profit achieved. 
Figure \ref{approximation} shows that, 
our 2-approximation algorithm achieves a ratio between 1 and 1.25 in real scenarios, 
and the average profit loss is around 10\%. 
This comes with a speedup by at least 100$\times$ under normal load (rate=6). 
 (more details can be seen in Appendix \ref{testbed-appendix}).
%Satisfaction percentage. It denotes the percentages of applications whose achieved availability is larger than the corresponding target.
%Figure \ref{availability_fig1}(b) shows 
%$\mathsf{BATE}$ performs about 20\%, 25\%, 30\%,  40\% better than TEAVAR, SMORE, SWAN, FFC, respectively.
%%Specially, when traffic scale is 3, more than 70\% applications can satisfy their availability demands, which is at least 30\% better than TEAVAR.
%Specially, the advantage of $\mathsf{BATE}$  is more obvious when there are resource competition (e.g., $s=3$).
%%The reason for this is that $\mathsf{BATE}$ considers the bandwidth-based availability demand differentiation of applications.
%This picture also demonstrates that the performance of $\mathsf{BATE}$ doesn't depend on particular network topology and traffic.
%Next, we take IBM trace as the example and perform the experiments.

@@

We compute the time ratio of the optimal solution and our greedy failure recovery algorithm for each scenario.
Figure \ref{sim-time}  shows that, under normal load (mean arrival rate=5$\sim$6), driving the optimal solution by bruce force is at least 100$\times$ slower than our greedy algorithm.
\end{appendices}
